\(Q\)-Boson model and relations with integrable hierarchies

### 2024-04-26 draft.tex
finish draft

\subsection{Scalar product: big Schur functions}

Let us now recover the result originally derived
in~\cite{Foda:2008hn} that shows how the scalar
product~(\ref{eq:scalar-hl}) is a tau function of the KP hierarchy.
From~\cite[see chap.3, sec. 4, eq. (4.7)]{Macdonald:1998}, we can
expand the Cauchy identity~(\ref{eq:cauchy_hl}) as
\begin{equation}
 \prod_{j, k=1}^\infty \frac{1-Q x_j y_k}{1 - x_j y_k} = 
\sum_{\lambda} \mathcal{S}_{\lambda}(\bm{x}, Q) s_{\lambda}(\bm{y}) =
\sum_{\lambda} \mathcal{S}_{\lambda}(\bm{y}, Q) s_{\lambda}(\bm{x}) \; ,
\end{equation}
where the polynomials \(\mathcal{S}_\lambda\), the big-Schur
functions, are given by a Jacobi-Trudi formula
\begin{equation}
  \mathcal{S}_{\lambda} (\bm{y}, Q) = \det(q_{\lambda_i -i + j}(\bm{y}, Q))\; , 
\end{equation}
and the coefficients \(q_m\) can be obtained from the following expression
\begin{equation}
 \sum_{m} q_m(\bm{y}, Q) z^m =
 \prod_{j} \frac{1-Q y_j z}{1 - y_j z}
\end{equation}
where \(z\) is a formal variable. It has been
argued~\cite{Foda:2008hn} in that if we interpret the big-Schur
functions as Plücker coordinates, the expression
\begin{equation}
  \mathcal{I}_Q(N,M | \bm{x}, \bm{y})
  = \sum_{\lambda \subseteq [N,M]} \mathcal{S}_{\lambda}(\bm{x}, Q) s_{\lambda}(\bm{y})
  = \sum_{\lambda \subseteq [N,M]} \mathcal{S}_{\lambda}(\bm{y}, Q) s_{\lambda}(\bm{x})\; ,
\end{equation}
is a restricted KP tau function with respect to both set of coordinates,
that is \(\bm{x}\) and \(\bm{y}\).

@@

\subsection{Kostka-Foulkes expansion}
Let us expand these polynomials in a Schur polynomials basis, that is
\begin{equation}
P_\lambda(\bm{x}, Q) = \sum_{\mu} K^{-1}_{\lambda \mu}(Q) s_\lambda(\bm{x})\; , 
\end{equation}
where \(K^{-1}_{\mu\nu}(Q) \in \mathbb{Z}[Q]\) are inverse
Kostka-Foulkes polynomials~\cite{Macdonald:1998, Wheeler:2018}.

Expanding now the big-Schur functions as
\begin{equation}
\label{eq:kf-exp}
  \mathcal{S}_\lambda(\bm{x}, Q) = \sum_{\mu} c_{\lambda\mu}(Q) s_\mu(\bm{x})\; ,
\end{equation}
we can fix the coefficients \(c_{\lambda\mu}\) in terms of Kostka-Foulkes
polynomials using the orthogonality relations of these polynomials~\cite{Macdonald:1998}. 
In particular, there is an inner product in the ring of symmetric functions such that
\begin{equation}
  \frac{1}{b_\mu}\langle P_\mu(\bm{x}, Q), P_\mu(\bm{x}, Q)\rangle = \langle
  \mathcal{S}_\mu(\bm{x}, Q), s_\mu(\bm{x})\rangle = \delta_{\mu\nu}\; .
\end{equation}
Therefore,
\begin{equation}
  \begin{split}
\delta_{\mu\nu} & = \sum_\lambda c_{\mu\lambda}  \langle s_\lambda(\bm{x}), s_\mu(\bm{x})\rangle\\
& = \sum_\lambda \sum_{\pi_1, \pi_2} c_{\mu\lambda}  K_{\lambda \pi_1} K_{\mu \pi_2}
\langle P_{\pi_1}(\bm{x}, Q), P_{\pi_2}(\bm{x}, Q)\rangle \\ 
& = \sum_\lambda \sum_{\pi} c_{\mu\lambda} b_{\mu}^{-1}  K_{\lambda \pi} K_{\mu \pi}\; ,
  \end{split}
\end{equation}
and we conclude that 
\begin{equation}
\label{eq:indices}
c_{\mu \nu} = \sum_\pi K_{\mu\pi}^{-1} b_\mu (K_{\nu\pi}^{-1})^T\; .
\end{equation}
\marginpar[left]{\tiny Fix these \\ indices later.}

Hence, we conclude that 
\begin{equation}
\sum_{\mu} S_{\mu}(\bm{x},Q) s_{\nu}(\bm{y}) = 
\sum_{\mu , \nu} c_{\mu\nu} s_{\mu}(\bm{x}) s_{\nu}(\bm{y}) 
\end{equation}
and everything boils down to the analysis of the
indices~(\ref{eq:indices}). In has been shown
in~\cite{Necoechea:2019wbg} that the big Schur functions themselves
are KP-tau functions\footnote{ We give a simple argument for this fact
in the remark 2 below.} therefore, the coefficients \((c_\lambda)_\mu
\equiv c_{\lambda\mu}\) must satisfy Plücker relations for the KP
hierarchy.

\begin{remark}
 This expression show somethign interesting. We can formulate this
problem in terms of partitions defined in the phase
model. Equivalently, we can use the usual vertex operator
construction, and not the q-deformed version of Jing~\emph{\cite{Jing1991,
  Jing1995}}, that is much harder to deal with.
\end{remark}

If these coefficients satisfy the Toda hierarchy Plücker relations, then 
one can find a \(Q\)-dependent group element \(G_Q\in GL(\infty)\) such that 
\begin{equation}
  c_{\mu\nu} = \bra{\mu} G_Q \ket{\nu}\; ,
\end{equation}
where \(\ket{\mu}\) and \(\ket{\nu}\) are phase model
states. Unfortunatelly, we could not find any good reason to explore
this expansion in a consistent way. In what follows, we try to explore
alternative expansions that give a double Schur expansion.

@@

\subsection{Scalar product: Supersymmetric Schur polynomials}

With this result, we now argue that~(\ref{eq:scalar-hl}) is also a tau
function of the Toda hierarchy in disguise. Let us decompose
\begin{equation}
 \sum_{m} q_m(\bm{y}, Q) z^m =
 \prod_j (1 + y_j (-Q z)) \prod_k (1 - y_k z)^{-1} = 
 \sum_{j, k} e_j(\bm{y}) h_k(\bm{y}) (- Q)^j z^{j+k}\; .
\end{equation}
And reorganizing this sum, we conclude that 
\begin{equation}
  q_m(\bm{y}, Q)  = \sum_{j=0}^m e_j(\bm{y}) h_{m-j}(\bm{y}) (- Q)^j =
 \sum_{j=0}^m e_j(-Q\bm{y}) h_{m-j}(\bm{y}) \; ,
\end{equation}
where in the last equality we have used the homogeneity of the elementary symmetric polynomials,
and \( -Q\bm{y} = (-Qy_1, -Qy_2, \dots)\).

It is easier to consider the following expansions 
\begin{subequations}
\begin{equation}
  \begin{split}
    \prod_{j=1}^N (1 - (Q y_i)z) & = \prod_{j=1}^N e^{ \ln  (1 - (Q y_i)z)} = 
    \prod_{j=1}^N \exp \left( - \sum_{n>0} \frac{Q^n y^n_j}{n} z^n \right) \\ 
    & = \exp \left( - \sum_{n>0} \sum_{j=1}^N \frac{Q^n y^n_j}{n} z^n \right)  =
    \exp \left( - \sum_{n>0} t^{(Q)}_n z^n \right)  
  \end{split}
\end{equation}
where \(t^{(Q)}_n = \frac{Q^n}{n} \sum_j y_j^n = Q^n t'_n\), and 
\begin{equation}
    \prod_{j=1}^N \frac{1}{(1 - y_iz)} = \prod_{j=1}^N e^{- \ln  (1 - y_iz)} = 
    \prod_{j=1}^N \exp \left( \sum_{n>0} \frac{y_j}{n} z^n \right)=
    \exp \left(\sum_{n>0} t_n z^n \right) \; . 
\end{equation}
\end{subequations}

Therefore 
\begin{equation}
 \sum_{m} q_m(\bm{y}, Q) z^m =
 \prod_j \frac{1 + y_j (-Q z)}{1 - y_k z}
 = \exp \left( \sum_{n\geq 1} (t'_n - t_n^{(Q)})z^n \right)
 \equiv \exp \left( \sum_{n\geq 1} T_n z^n \right)\; ,
\end{equation}
with \(T_n = (1 - Q^n) t'_n\). Then, we conclude that \(q_m(\bm{y}, Q)\)
are homogeneous polynomials with respect the Miwa coordinates
\(\bm{T} = (T_1, T_2, \dots)\). Then
\begin{equation}
  \mathcal{S}_\lambda(\bm{t}', Q) = \det \left(h_{\lambda_i - i +j}(\bm{T})\right) = s_\lambda(\bm{T})\; .
\end{equation}
All in all, we conclude that the big Schur functions
\(S_\lambda(\bm{t}', Q)\) are ordinary Schur functions with respect
the coordinates \(\bm{T}\).

In fact, we can do even better. Supersymmetric (or Hook) Schur
functions~\cite{Berele:1983}, see also see~\cite{Macdonald:1998, Moens:2003},
\(s_\lambda(\bm{\alpha}/\bm{\beta})\) are defined as ordinary schur
functions evaluated at Miwa coodinates of the form
\begin{equation}
  T_n = \frac{1}{n} \left( \sum_{i=1}^{\dim(\alpha)} \alpha_i^n
       - \sum_{i=1}^{\dim(\beta)} (-\beta_i)^n\right)\; ,
\end{equation}
and comparing with the results above, we can see that the big Schur functions
\(S_\lambda(\bm{t}', Q)\)\; , is the supersymmetric Schur functions for \(\bm{\alpha} = \bm{y}\) 
and \(\bm{\beta} = - Q \bm{y}\), that is 
\begin{equation}
  S_\lambda(\bm{t}', Q) = s_\lambda[\bm{y}/(- Q\bm{y})]\; .
\end{equation}

Putting these facts together, we immediately conclude that since 
\begin{equation}
  \sum_\lambda s_\lambda(\bm{T}) s_\lambda (\bm{t}) \; ,
\end{equation}
is a Toda hierarchy tau function, we obviously have that 
\begin{equation}
  S_Q(N,M| \bm{x}, \bm{y}) \equiv S_Q(N,M| \bm{t}, \bm{T})
  = \sum_{\lambda \subseteq [N,N,M]} s_\lambda(\bm{T}) s_\lambda(\bm{t})\; , 
\end{equation}
is also a restricted tau function of the Toda hierarchy with respect
to \(\bm{t}\) and \(\bm{T}\).

Now we can consider an expansion that differs from
from~(\ref{eq:kf-exp}). Let us consider the supersymmetric Schur
polynomials in terms of ordinary Schur functions as~\cite[Sec. I.5,
  exerc. 23]{Macdonald:1998}
\begin{equation}
  s_{\lambda}(\bm{x}/\bm{y}) = \sum_\mu s_{(\lambda/\mu)'}(\bm{y}) s_\mu(\bm{x})\; ,
\end{equation}
where the prime denotes the conjugate diagram. Then
\begin{equation}
  \label{eq:tau-hl}
  \sum_{\lambda } s_\lambda(\bm{y}/ (- Q\bm{y})) s_\lambda(\bm{x}) =
  \sum_{\lambda,\mu } s_{(\lambda/\mu)'}(- Q\bm{y}) s_\lambda(\bm{x}) s_\mu(\bm{y})\; .
\end{equation}

@@

\begin{remark}
Since the skew Schur polynomials have determinant expressions,
therefore we have that the \(\bm{y}\)-dependent coefficients \(c_{\mu
  \lambda} = s_{(\lambda/\mu)'}(-Q\bm{y})\) have Jacobi-Trudi
expressions. It is tempting to think of these objects as
\(\bm{y}\)-dependent Pl\"ucker coordinates. In this sense, we would have a curve in 
the indinite Grassmannian, instead a point.
\end{remark}

\begin{remark}
Remeber that one of the easiest nontrivial solutions of the KP
hierarchies are the Schur functions
themselves~\emph{\cite{Zabrodin2018}}. We have just seen that the
big-Schur polynomials can be written as supersymmetric Shur
polynomials, and these are nothing but ordinary Schur polynomials in a
particular choice of Miwa coordiantes. Then, we also see that 
the big Schur polynomials are also KP tau functions. This direct conclusion 
is an alternative proof of this fact, see~\emph{\cite{Necoechea:2019wbg}}.
\end{remark}

Putting these facts together, we have that the left-hand side
of~(\ref{eq:tau-hl}) is a tau function with respect the coordinates
\(\bm{T}\) and \(\bm{t}\). Furthermore, from the Vertex operator
formalism, we write the Schur polynomials as
\begin{equation}
  s_{\lambda}(\bm{x}) = \bra{\lambda} e^{J_-}\ket{\bm{0}}\qquad
  s_{\mu}(\bm{y}) = \bra{\bm{0}} e^{J_+}\ket{\mu}\; ,
\end{equation}
we have
\begin{equation}
  \sum_{\lambda,\mu } s_\mu(\bm{y})c_{\mu\lambda}(Q,\bm{y}) s_\lambda(\bm{x}) = 
  \sum_{\lambda,\mu } \bra{\bm{0}} e^{J_+}\ket{\mu} c_{\mu\lambda}(Q,\bm{y})
  \bra{\lambda} e^{J_-}\ket{\bm{0}} \; ,
\end{equation}
therefore 
\begin{equation}
  c_{\mu\lambda}(Q, \bm{y}) = \bra{\mu} G_Q(\bm{y}) \ket{\lambda}\; ,
\end{equation}
where \(G_Q(\bm{y}) \in GL(\infty)\). We can find the expression for
this group element as follows.

Remember that \(T_m = t'_m - Q^m t'_m\), therefore we write
\begin{subequations}
\begin{equation}
  \bra{\bm{0}} e^{J_+(\bm{t})} e^{J_-(\bm{T})} \ket{\bm{0}} = 
\bra{\bm{0}} e^{J_+(\bm{t})} e^{J_-(\bm{t}')  - J_-(\bm{t}^{(Q)})} \ket{\bm{0}} \; .
\end{equation}
From the Heisenberg algebra, we conclude that \([J_-(\bm{t}),
  J_-(\bm{t}')] = 0\), therefore
\begin{equation}
  \bra{\bm{0}} e^{J_+(\bm{t})} e^{J_-(\bm{T})} \ket{\bm{0}} = 
\bra{\bm{0}} e^{J_+(\bm{t})} e^{-J_-(\bm{t}^{(Q)})} e^{J_-(\bm{t}')}  \ket{\bm{0}} \; ,
\end{equation}
\end{subequations}
from where we finally conclude that 
\begin{equation}
  G_{Q}(\bm{y}) = \exp \left(-J_-(\bm{t}^{(Q)})\right) \qquad
  t^{(Q)}_n = \frac{Q^n}{n}\sum_j y_j^n\; . 
\end{equation}

In general, the expectation values with coordinate dependent group
elements \(G_{Q}(\bm{y})\) are not Toda hierarchy tau functions. But
in the above example, the coordinates combine among themselves and
generate a tau function with respect the coordiantes \(\bm{T}\) and
\(\bm{t}\).

@@

Let us now consider the fermionic construction of this tau function. We write 
the limit \(N,M\to \infty\) of the scalar product
\begin{subequations}
\begin{equation}
  S_Q(\bm{T}, \bm{t}') = \sum_{\mu} s_\mu(\bm{T}) s_\mu(\bm{t}')
\end{equation}
that is quite quite trivial from the viewpoint of the free fermion construction, 
\begin{equation}
  S_Q(\bm{T}, \bm{t}') = \bra{\bm{0}} e^{\bm{J}_+(\bm{T})} e^{\bm{J}_-(\bm{t}')} \ket{\bm{0}}\; .
\end{equation}

Moreover, we also know that
\begin{equation}
  S_Q(\bm{t}, \bm{t}') = \sum_{\mu\nu} c_{\mu\nu} s_\mu(\bm{t}) s_\mu(\bm{t}')
\end{equation}
where \(n t = \sum_j x^n_j\) and \(n t' = \sum_j y^n_j\) are Miwa coordinates, then  
\begin{equation}
  S_Q(\bm{t}, \bm{t}') = \bra{\bm{0}} e^{J_+(\bm{t})} G_Q  e^{J_-(\bm{t}')} \ket{\bm{0}}
\end{equation}
and \(G_Q \in GL(\infty)\) that depends on \(Q\). We could also think of \(G_Q\)
as a twist
\(G_Q = e^{Q H} G e^{-Q H}\), with the action of \(H\in \mathfrak{gl}(\infty)\)
on ordinary fermions generating the Q-fermions. 
\marginpar[left]{\tiny Investigate this\\ twists}
\end{subequations}

It seems that we have some different representations for this tau function, 
and it is worth investigating what is happening here. That is what we want 
to do now.

>>>>

\subsection{Big Schur functions expansion}
Now, let's revisit the result originally derived in~\cite{Foda:2008hn}
which demonstrates that the scalar product~(\ref{eq:scalar-hl}) is a
tau function of the KP hierarchy. According to~\cite[Chapter 3,
  Section 4, Equation (4.7)]{Macdonald:1998}, we can expand the Cauchy
identity~(\ref{eq:cauchy_hl}) as
\begin{equation}
 \prod_{j, k=1}^\infty \frac{1-Q x_j y_k}{1 - x_j y_k} = 
\sum_{\lambda} \mathcal{S}_{\lambda}(\bm{x}, Q) s_{\lambda}(\bm{y}) =
\sum_{\lambda} \mathcal{S}_{\lambda}(\bm{y}, Q) s_{\lambda}(\bm{x}) \; .
\end{equation}
Here, the polynomials \(\mathcal{S}_\lambda\), known as the big-Schur
functions, are defined by a Jacobi-Trudi formula:
\begin{equation}
  \mathcal{S}_{\lambda} (\bm{y}, Q) = \det(q_{\lambda_i -i + j}(\bm{y}, Q))\; , 
\end{equation}
and the coefficients \(q_m\) are obtained from the expression:
\begin{equation}
 \sum_{m} q_m(\bm{y}, Q) z^m =
 \prod_{j} \frac{1-Q y_j z}{1 - y_j z}\; .
\end{equation}
where \(z\) is a formal variable. It has been
argued~\cite{Foda:2008hn} in that if we interpret the big-Schur
functions as Plücker coordinates, the expression
\begin{equation}
\label{eq:big-expansion}
  \mathcal{I}_Q(N,M | \bm{x}, \bm{y})
  = \sum_{\lambda \subseteq [N,M]} \mathcal{S}_{\lambda}(\bm{x}, Q) s_{\lambda}(\bm{y})
  = \sum_{\lambda \subseteq [N,M]} \mathcal{S}_{\lambda}(\bm{y}, Q) s_{\lambda}(\bm{x})\; ,
\end{equation}
is a restricted KP tau function with respect to both set of coordinates,
that is \(\bm{x}\) and \(\bm{y}\).

Based on these findings, we conclude that the inner product can be
expressed as a quotient of two Toda tau functions or as a KP tau
function with coefficients given by the big Schur
polynomials. However, further exploration of these results is
warranted.

@@

\subsection{Kostka-Foulkes expansion}
In a Schur polynomial basis, we write
\begin{equation}
P_\lambda(\bm{x}, Q) = \sum_{\mu} K^{-1}_{\lambda \mu}(Q) s_\lambda(\bm{x})\; , 
\end{equation}
where \(K^{-1}_{\mu\nu}(Q) \in \mathbb{Z}[Q]\) are inverse
Kostka-Foulkes polynomials~\cite{Macdonald:1998, Wheeler:2018}.

If we now insert this expansion in the inner product, we have 
\begin{equation}
    \sum_\lambda b_\lambda(Q) P_\lambda(\bm{x}, Q) P_\lambda(\bm{y}, Q) = 
    \sum_{\mu,\nu} \left(\sum_\lambda K_{\mu \lambda}^{-1 \; T} b_\lambda(Q)  K_{\lambda \nu}^{-1} \right)
    s_{\mu}(\bm{x}) s_{\nu}(\bm{y}) 
\end{equation}
and we have the coefficients 
\begin{equation}
\label{eq:c-expan}
 \tilde{c}_{\mu\nu}(Q) = \sum_\lambda K_{\mu \lambda}^{-1 \; T} b_\lambda(Q)  K_{\lambda \nu}^{-1} \; ,
\end{equation}
for the double expansion of the inner product in terms of Schur
polynomials. Based on our discussion so far, we know that these
coefficients are not Plücker coordinates of the Toda hierarchy.

But we can say something interesting about these coefficients. Let us
now expand the big-Schur functions as
\begin{equation}
\label{eq:kf-exp}
  \mathcal{S}_\mu(\bm{x}, Q) = \sum_{\lambda} \mathcal{C}^{\mu}_\lambda(Q) s_\lambda(\bm{x})\; ,
\end{equation}
we can fix the coefficients \(\mathcal{C}_\lambda^\mu(Q)\) in terms of
Kostka-Foulkes polynomials using the orthogonality relations of these
polynomials~\cite{Macdonald:1998}. In particular, there is an inner
product in the ring of symmetric functions such that
\begin{equation}
  b_\mu \langle P_\mu(\bm{x}, Q), P_\nu(\bm{x}, Q)\rangle = \langle
  \mathcal{S}_\mu(\bm{x}, Q), s_\nu(\bm{x})\rangle = \delta_{\mu\nu}\; .
\end{equation}
Therefore,
\begin{equation}
  \begin{split}
\delta_{\mu\nu} & = \sum_\lambda \mathcal{C}_\lambda^\mu \langle s_\lambda(\bm{x}), s_\nu(\bm{x})\rangle
 = \sum_\lambda \sum_{\pi, \sigma} \mathcal{C}_\lambda^\mu K_{\lambda \pi} K_{\nu \sigma}
\langle P_{\pi}(\bm{x}, Q), P_{\sigma}(\bm{x}, Q)\rangle \\ 
& = \sum_\lambda \mathcal{C}_\lambda^\mu \sum_{\sigma}K_{\lambda \sigma} b_{\sigma}^{-1} K_{\nu \sigma}\; ,
  \end{split}
\end{equation}
and we conclude that 
\begin{equation}
\label{eq:indices}
(\mathcal{C}^{-1})^\lambda_\nu = \sum_\sigma K_{\lambda\sigma} b^{-1}_\sigma (K_{\sigma\nu})^T\; ,
\end{equation}
and consistency with~(\ref{eq:c-expan}) implies that
\(\mathcal{C}^\lambda_\nu \equiv \tilde{c}_{\lambda\nu}\).

Hence, we conclude that 
\begin{equation}
S_{\mu}(\bm{t},Q) = \sum_{\nu} \tilde{c}_{\mu\nu}(Q) s_{\mu}(\bm{t})\; ,
\end{equation}
where we have written the big Schur polynomial in terms of the Miwa
coordinates \(\bm{t}\).

\begin{remark}
This expression also reveals something interesting. We can formulate
this problem in terms of partitions defined in the phase
model. Alternatively, we can utilize the conventional vertex operator
construction rather than the q-deformed version proposed by
Jing~\cite{Jing1991, Jing1995}, which is much more challenging to
handle.
\end{remark}

@@

\subsection{Supersymmetric Schur polynomials expansion}
With this result, we now argue that although~(\ref{eq:scalar-hl}) is
not a Toda tau function with respect to the coordinates \(\{\bm{t};
\bm{t}'\}\), we can define a new set of coordinates
\(\{\bm{t};\bm{T}\}\) that render the inner product a trivial Toda tau
function.

Let us first decompose
\begin{equation}
 \sum_{m} q_m(\bm{y}, Q) z^m =
 \prod_j (1 + y_j (-Q z)) \prod_k (1 - y_k z)^{-1} = 
 \sum_{j, k} e_j(\bm{y}) h_k(\bm{y}) (- Q)^j z^{j+k}\; .
\end{equation}
Reorganizing this sum, we conclude that
\begin{equation}
  q_m(\bm{y}, Q)  = \sum_{j=0}^m e_j(\bm{y}) h_{m-j}(\bm{y}) (- Q)^j =
 \sum_{j=0}^m e_j(-Q\bm{y}) h_{m-j}(\bm{y}) \; ,
\end{equation}
where in the last equality we have used the homogeneity of the
elementary symmetric polynomials, and \( Q\bm{y} \equiv (Qy_1, Qy_2,
\dots)\).

It is easy to see that
\begin{subequations}
\begin{equation}
  \begin{split}
    \prod_{j=1}^N (1 - (Q y_j)z) & = \prod_{j=1}^N e^{ \ln  (1 - (Q y_j)z)} = 
    \prod_{j=1}^N \exp \left( - \sum_{n>0} \frac{Q^n y^n_j}{n} z^n \right) \\ 
    & = \exp \left( - \sum_{n>0} \sum_{j=1}^N \frac{Q^n y^n_j}{n} z^n \right)  =
    \exp \left( - \sum_{n>0} t^{(Q)}_n z^n \right)  
  \end{split}
\end{equation}
where \(t^{(Q)}_n = \frac{Q^n}{n} \sum_j y_j^n = Q^n t'_n\). Additionally
\begin{equation}
    \prod_{j=1}^N \frac{1}{(1 - y_jz)} = \prod_{j=1}^N e^{- \ln  (1 - y_jz)} = 
    \prod_{j=1}^N \exp \left( \sum_{n>0} \frac{y_j}{n} z^n \right)=
    \exp \left(\sum_{n>0} t_n z^n \right) \; . 
\end{equation}
\end{subequations}

Consequently
\begin{equation}
 \sum_{m} q_m(\bm{y}, Q) z^m =
 \prod_j \frac{1 - Q y_j z}{1 - y_k z}
 = \exp \left( \sum_{n\geq 1} (t'_n - t_n^{(Q)})z^n \right)
 \equiv \exp \left( \sum_{n\geq 1} T_n z^n \right)\; ,
\end{equation}
with \(T_n = (1 - Q^n) t'_n\). Then, we conclude that \(q_m(\bm{y}, Q)\)
are homogeneous polynomials with respect the Miwa coordinates
\(\bm{T} = (T_1, T_2, \dots)\). Then
\begin{equation}
  \mathcal{S}_\lambda(\bm{t}', Q) = \det \left(h_{\lambda_i - i +j}(\bm{T})\right) = s_\lambda(\bm{T})\; .
\end{equation}
All in all, we conclude that the big Schur functions
\(S_\lambda(\bm{t}', Q)\) are ordinary Schur functions with respect to
the coordinates \(\bm{T}\).

Moreover, a more refined approach is also possible. Supersymmetric (or
Hook) Schur functions~\cite{Berele:1983}, as discussed in works such
as~\cite{Macdonald:1998, Moens:2003}, denoted by
\(s_\lambda(\bm{\alpha}/\bm{\beta})\), are defined as ordinary Schur
functions evaluated at Miwa coordinates of the form
\begin{equation}
  T_n = \frac{1}{n} \left( \sum_{i=1}^{\dim(\alpha)} \alpha_i^n
       - \sum_{i=1}^{\dim(\beta)} (-\beta_i)^n\right)\; .
\end{equation}
Comparing this expression with the results above, we can see that the
big Schur functions \(S_\lambda(\bm{t}', Q)\) correspond to the
supersymmetric Schur functions for \(\bm{\alpha} = \bm{y}\) and
\(\bm{\beta} = - Q \bm{y}\), which is
\begin{equation}
  S_\lambda(\bm{t}', Q) = s_\lambda[\bm{y}/(- Q\bm{y})]\; .
\end{equation}

Putting these facts together, we immediately conclude that
\begin{equation}
\lim_{M,N\to \infty}\mathcal{I}_Q(N,M|\bm{x}, \bm{y}) = 
  \sum_\lambda s_\lambda(\bm{T}) s_\lambda (\bm{t})
\end{equation}
is a Toda hierarchy tau function with respect to
\(\{\bm{t};\bm{T}\}\). As a result, we obviously have that
\begin{equation}
  \mathcal{I}_Q(N,M| \bm{x}, \bm{y}) \equiv \mathcal{I}_Q(N,M| \bm{t}, \bm{T})
  = \sum_{\lambda \subseteq [N,M]} s_\lambda(\bm{T}) s_\lambda(\bm{t})
\end{equation}
is also a restricted tau function of the Toda hierarchy with respect
to \(\bm{t}\) and \(\bm{T}\).

Let us also express the supersymmetric Schur polynomials in terms of
ordinary Schur functions, as shown in~\cite[Sec. I.5, exerc. 23]{Macdonald:1998}:
\begin{equation}
  s_{\lambda}(\bm{x}/\bm{y}) = \sum_\mu s_{(\lambda/\mu)'}(\bm{y}) s_\mu(\bm{x})\; ,
\end{equation}
where the prime denotes the conjugate diagram. Compare this expansion
with~(\ref{eq:kf-exp}). Then
\begin{equation}
  \label{eq:tau-hl}
  \sum_{\lambda } s_\lambda(\bm{T}) s_\lambda(\bm{t}) =
  \sum_{\lambda,\mu } s_{(\lambda/\mu)'}(- Q\bm{y}) s_\lambda(\bm{t}) s_\mu(\bm{t}')\; .
\end{equation}

@@

\begin{remark}
Since the skew Schur polynomials have determinant expressions, we can
deduce that the \(\bm{y}\)-dependent coefficients \(c_{\mu \lambda} =
s_{(\lambda/\mu)'}(-Q\bm{y})\) have Jacobi-Trudi expressions. It is
tempting to regard these objects as \(\bm{y}\)-dependent Plücker
coordinates. In this sense, we would have a curve in the infinite
Grassmannian instead of a point.
\end{remark}

\begin{remark}
It is worth noting that one of the simplest nontrivial solutions of
the KP hierarchies are the Schur functions
themselves~\emph{\cite{Zabrodin2018}}. As we have just demonstrated, the big
Schur polynomials can be expressed as supersymmetric Schur
polynomials, which are essentially ordinary Schur polynomials in a
specific choice of Miwa coordinates. Therefore, we conclude that the
big Schur polynomials are also KP tau functions. This direct
conclusion serves as an alternative proof of this fact, originally derived in
in~\emph{\cite{Necoechea:2019wbg}} using the KP bilinear identity.
\end{remark}

Combining these observations, we conclude that the left-hand side of
equation (\ref{eq:tau-hl}) serves as a tau function with respect to
the coordinates \(\{\bm{t}; \bm{T}\}\). Additionally, utilizing the
vertex operator formalism, we can express the Schur polynomials as
\begin{equation}
  s_{\lambda}(\bm{t}') = \bra{\lambda} e^{J_-(\bm{t}')}\ket{\bm{0}}\qquad
  s_{\mu}(\bm{t}) = \bra{\bm{0}} e^{J_+(\bm{t})}\ket{\mu}\; ,
\end{equation}
we have
\begin{equation}
  \sum_{\lambda,\mu } c_{\mu\lambda}(Q,\bm{y}) s_\mu(\bm{t}') s_\lambda(\bm{t}) = 
  \sum_{\lambda,\mu } \bra{\bm{0}} e^{J_+(\bm{t})}\ket{\mu} c_{\mu\lambda}(Q,\bm{y})
  \bra{\lambda} e^{J_-(\bm{t}')}\ket{\bm{0}} \; .
\end{equation}
It is important to emphasize once again that this expression does not
constitute a tau function with respect to \(\{\bm{t},
\bm{t}'\}\). Despite this crucial distinction, we proceed under the
assumption that the coefficients can be expressed as
\begin{equation}
  c_{\mu\lambda}(Q, \bm{y}) = \bra{\mu} G_Q(\bm{y}) \ket{\lambda}\; ,
\end{equation}
where \(G_Q(\bm{y}) \in GL(\infty)\). Hence
\begin{equation}
  \lim_{N,M\to\infty} \mathcal{I}_Q(N, M| \bm{t}, \bm{t}'(\bm{y})) = 
  \bra{\bm{0}} e^{J_+(\bm{t})} G_Q(\bm{y}) e^{J_-(\bm{t}')}\ket{\bm{0}}\; .
\end{equation}
where \(t'_n = \frac{1}{n}\sum_i y_i^n\).

To derive the expression for this group element, recall that \(T_m =
t'_m - Q^m t'_m\). With this in mind, we can express the scalar
product as follows:
\begin{subequations}
\begin{equation}
  \bra{\bm{0}} e^{J_+(\bm{t})} e^{J_-(\bm{T})} \ket{\bm{0}} = 
\bra{\bm{0}} e^{J_+(\bm{t})} e^{J_-(\bm{t}')  - J_-(\bm{t}^{(Q)})} \ket{\bm{0}} \; .
\end{equation}
From the Heisenberg algebra, we deduce that \([J_-(\bm{t}),
  J_-(\bm{t}')] = 0\), therefore
\begin{equation}
  \bra{\bm{0}} e^{J_+(\bm{t})} e^{J_-(\bm{T})} \ket{\bm{0}} = 
\bra{\bm{0}} e^{J_+(\bm{t})} e^{-J_-(\bm{t}^{(Q)})} e^{J_-(\bm{t}')}  \ket{\bm{0}} \; .
\end{equation}
\end{subequations}
We finally conclude that 
\begin{equation}
  G_{Q}(\bm{y}) = \exp \left(-J_-(\bm{t}^{(Q)})\right) \qquad
  t^{(Q)}_n = \frac{Q^n}{n}\sum_j y_j^n\; . 
\end{equation}

Generally, the expectation values involving coordinate-dependent group
elements \(G_{Q}(\bm{y})\) do not form Toda hierarchy tau
functions. However, in the example above, the coordinates combine in
such a way that they generate a tau function with respect to the
coordinates \(\bm{T}\) and \(\bm{t}\).

@@

%Let us now consider the fermionic construction of this tau function. We write 
%the limit \(N,M\to \infty\) of the scalar product
%\begin{subequations}
%\begin{equation}
%  S_Q(\bm{T}, \bm{t}') = \sum_{\mu} s_\mu(\bm{T}) s_\mu(\bm{t}')
%\end{equation}
%that is quite quite trivial from the viewpoint of the free fermion construction, 
%\begin{equation}
%  S_Q(\bm{T}, \bm{t}') = \bra{\bm{0}} e^{\bm{J}_+(\bm{T})} e^{\bm{J}_-(\bm{t}')} \ket{\bm{0}}\; .
%\end{equation}
%
%Moreover, we also know that
%\begin{equation}
%  S_Q(\bm{t}, \bm{t}') = \sum_{\mu\nu} c_{\mu\nu} s_\mu(\bm{t}) s_\mu(\bm{t}')
%\end{equation}
%where \(n t = \sum_j x^n_j\) and \(n t' = \sum_j y^n_j\) are Miwa coordinates, then  
%\begin{equation}
%  S_Q(\bm{t}, \bm{t}') = \bra{\bm{0}} e^{J_+(\bm{t})} G_Q  e^{J_-(\bm{t}')} \ket{\bm{0}}
%\end{equation}
%and \(G_Q \in GL(\infty)\) that depends on \(Q\). We could also think of \(G_Q\)
%as a twist
%\(G_Q = e^{Q H} G e^{-Q H}\), with the action of \(H\in \mathfrak{gl}(\infty)\)
%on ordinary fermions generating the Q-fermions. 
%\marginpar[left]{\tiny Investigate this\\ twists}
%\end{subequations}
%
%It seems that we have some different representations for this tau function, 
%and it is worth investigating what is happening here. That is what we want 
%to do now.
